Synthesizing Quotient Lenses

### 2017-10-17 papers/QuotientLensSynth/main.tex
add in some hard data

\item \afm{10} of our benchmarks were derived from data.gov.  Data.gov contains
  many transformations between formats.  In addition to the formats previously
  adopted for Optician, we synthesized transformers between these formats.
\end{enumerate}

@@

We found that \afm{35} of Opticians 39 benchmarks required modifications to be
bijective when put in canonical form. We found that \afm{25} of Optician's 39
benchmarks required modifications to be in bijective correspondence when in
canonical form.  Furthermore, we found that \afm{all} of the data.gov examples
required no modifications to be in canonical form.  While we did not put the
data.gov examples into a form suitable for Optician, we found only \afm{1} of
the \afm{5} data.gov examples did not require canonization, so making suitable
for Optician would have required a modification of \afm{4} of the data.gov
examples.

@@

We summarize the results of these experiments in Figure~\ref{?}.  \Name{} was
able to synthesize all of Optician's benchmarks at a competitive speed with
Optician.  Furthermore, adopting these tasks to use QREs actually sped up
tasks!  After canonization, the regular expressions sent to synthesis are
\emph{smaller} than before canonization - making the bijective lens synthesis
portion of these tasks easier.

>>>>

\item \afm{8} of our benchmarks were derived from data.gov.  Data.gov contains
  many transformations between formats.  In addition to the formats previously
  adopted for Optician, we synthesized transformers between these formats.
\end{enumerate}

@@

We found that 10 of Opticians 39 benchmarks required modifications to be
bijective. We found that 4 of Optician's 39
benchmarks required modifications to be in bijective correspondence when in
canonical form.  Furthermore, we found that all of the data.gov examples
required no modifications to be in canonical form.  While we did not put the
data.gov examples into a form suitable for Optician, we found only 4 of
the 8 data.gov examples did not require canonization, so making suitable
for Optician would have required a modification of 4 of the data.gov
formats.

@@

We summarize the results of these experiments in Figure~\ref{?}.  \Name{} was
able to synthesize all of Optician's benchmarks at a speed competitive with
Optician.  Furthermore, adopting these tasks to use QREs actually sped up
tasks!  After canonization, the regular expressions sent to synthesis are
\emph{smaller} than before canonization - making the bijective lens synthesis
portion of these tasks easier.
